### 2013-10-17 chi2014/related.tex
10 page revision first attempt

Following Osborne's work, Taylor et al.\ established that brainstorming by \emph{nominal groups}, or individuals working in isolation from one another, yields better results than collocated groups in terms of number of ideas generated \cite{taylor_does_1958}. These effects can be partially explained by the absence of counterproductive social forces, such as production blocking (the inability for multiple people to speak at once) and the fear of judgment. Bouchard and Hare \cite{bouchard_jr_size_1970} later found that nominal brainstorming groups are able to generate quantities of ideas linear in the number of members in the group.

Electronic brainstorming is a variant in which individuals brainstorm at separate computer terminals, with the exchange of ideas performed over the network \cite{gallupe_electronic_1992}. Participants can enter ideas while simultaneously viewing the ideas of all other ideas, which are anonymously presented on-screen. As with nominal brainstorming, Gallupe \cite{gallupe_electronic_1992} observed that electronic brainstorming can reduce counterproductive social effects. However, Pinsonneault et al.\ \cite{pinsonneault_electronic_1999} identify productivity impediments introduced by group electronic brainstorming, such as being distracted by other ideas appearing, and individuals witholding ideas they feel are derivative of others. Given these drawbacks, their results suggest there is little evidence to support the proposition that electronic brainstorming outperforms nominal brainstorming.

Finally, Diehl and Stroebe found that groups that generate good ideas also generate \emph{many} ideas \cite{diehl_productivity_1987}, a finding that has been verified many times \cite{briggs1997quality, parnes1959effects, parnes_effects_1961, shah2003metrics, cross1996creativity}.

Shifting our focus to an \emph{individual's} brainstorming processes, Nijstad and Stroebe provide a model for individual idea generation dubbed SIAM, or the ``search for ideas in associative memory'' \cite{nijstad_how_2006}. SIAM defines two stages of idea generation: the generation of ideas based on working memory, and idea production within a single activated ``image'' (where an image can be thought of as a category of ideas). This model makes predictions applicable to all brainstorming contexts, with one of the most important predictions being that an idea is more likely to be followed by an idea in the same category than would be expected by chance. Their model also predicts that new ideas in the same category as the previous idea are generated faster than ideas between categories. Nijstad and Stroebe verified these predictions in the context of nominal brainstorming.

@@

The most common approach to measure novelty and appropriateness is to ask domain experts to subjectively make scale-rated assessment of each \cite{lewis2011affective, amabile_1983}. Depending on the types of artifacts and researchers' interest, these two measures are sometimes combined into one measure of quality \cite{little2010exploring}.

Instead of subjective ratings, some researchers opt for a measure that can be derived objectively. For example, Jansson et al. used `o' scores, derived from the frequency with which an idea occurs, to evaluate products novelty \cite{jansson_design_1991}. We adopt this use of o-score in our later analyses.

Flexibility is often measured by the number of explored ``categories'' in a design space, or by subjective rating from domain experts \cite{lewis2011affective, marsh1996examples}. Category or feature-based quantities also yield other metrics such as within-categories fluency and the length of train-of-thought when participants focus on a particular category \cite{nijstad_how_2006}. Building in this past line of work, we consider both individual ideas and categories of ideas.

\subsection{Crowdsourced Brainstorming}
The simplest imaginable instantiation of brainstorming in a microtask marketplace mirrors that of nominal brainstorming. More sophisticated brainstorming environments are possible, such as those that provide awareness of ideas that others have generated (electronic brainstorming), or those that rely on the crowd to organize or rank the ideas produced by others, as in evolutionary techniques \cite{yu_cooks_2011}.
%Examples for these environments are platforms for generating social innovation ideas or product concepts like OpenIDEO, Quirky and Threadless that employ structured process where participants take on different responsibility from generating ideas to evaluating others' ideas.
In this paper, we constrain our focus to nominal brainstorming in this environment with the goal of establishing a set of baselines.

While we are unaware of specific studies of brainstorming in microtask marketplaces, there is a range of related research examining other creative processes \cite{lewis2011affective, kittur2011crowdforge, Zhang:2012:HCT:2207676.2207708}. For example, Yu and Nickerson created an evolutionary crowd algorithm to generate creative chair designs \cite{yu_cooks_2011}. Their work demonstrates the creative potential of the crowd, but does not specifically address brainstorming or analogous processes in which participants generate many ideas.

Little et el. compared the iterative and parallel human computation processes on a brainstorming task for names for fabricated companies \cite{little2010exploring}. In the iterative condition, participants saw all names suggested by previous participants. Participants in the parallel condition worked in isolation without seeing other participants' ideas. Subjective ratings of the quality of ideas reveal that while the ideas from the iterative condition were rated higher on average, the best ideas from the parallel condition were rated higher than the best ideas from the iterative conditions. Thus, the parallel process was found to be more likely to generate names with high ratings, advocating the case for nominal brainstorming over traditional electronic brainstorming. However, the study did not mention categorization of generated ideas, an important measure on flexibility of idea generation \cite{lewis2011affective, nijstad_how_2006, finke1992creative, shah2003metrics}. Each participant also generated only five ideas, leaving the number of ideas requested per participant an open dimension to be explored.

The nature of the microtask marketplace may also require alternative ways of structuring the brainstorming activity in this environment.
% calls for an alternative structure for brainstorming tasks in this setting. Researchers have found that 30\% or more submission on Mechanical Turk may be low quality \cite{kittur2008crowdsourcing}. For example, submissions to a brainstorming task for a company name are sometimes grammartically awkward or offensive \cite{little2010exploring}. These low quality responses were not found in walk-in brainstorming studies. 
For example, Bernstein et al. found high variance of effort from Amazon Mechanical Turk workers \cite{soylent}. They characterized two worker personas at opposite ends of the effort spectrum: the {\em Eager Beaver\/} who goes beyond task requirement and the {\em Lazy Turker\/} who does as little work as necessary to get paid. Given this finding, a brainstorming task that asks participants to generate as many ideas as they can in a fixed time period might not be cost-effective, since a {\em Lazy Turker\/} can simply fill in a few ideas and wait for the time to run out instead of exerting full effort.

@@

In summary, while brainstorming has been examined in traditional and electronic settings, its application in crowd marketplaces has received limited attention, leaving many open questions about how this process occurs in this environment.

>>>>

Following Osborne's work, Taylor et al.\ established that brainstorming by \emph{nominal groups}, or individuals working in isolation from one another, yields better results than collocated groups in terms of number of ideas generated \cite{taylor_does_1958}. These effects can be partially explained by the absence of counterproductive social forces, such as fear of judgment. Bouchard and Hare \cite{bouchard_jr_size_1970} later found that nominal brainstorming groups are able to generate quantities of ideas linear in the number of members in the group.

Electronic brainstorming is a variant in which individuals brainstorm at separate computer terminals, with the exchange of ideas performed over the network \cite{gallupe_electronic_1992}. Participants enter ideas while others' ideas are anonymously presented on-screen. As with nominal brainstorming, Gallupe \cite{gallupe_electronic_1992} observed that electronic brainstorming can reduce counterproductive social effects. However, Pinsonneault et al.\ \cite{pinsonneault_electronic_1999} identify productivity impediments introduced by group electronic brainstorming, such as being distracted by other ideas appearing, and individuals witholding ideas they feel are derivative of others. They find little evidence to support the proposition that electronic brainstorming outperforms nominal brainstorming.

Finally, Diehl and Stroebe found that groups that generate many ideas also generate \emph{good} ideas \cite{diehl_productivity_1987}, a finding that has been verified many times \cite{briggs1997quality, parnes1959effects, parnes_effects_1961, shah2003metrics, cross1996creativity}.

Shifting our focus to an \emph{individual's} brainstorming processes, Nijstad and Stroebe provide a model for individual idea generation dubbed SIAM, or the ``search for ideas in associative memory'' \cite{nijstad_how_2006}. SIAM defines two stages of idea generation: the generation of ideas based on working memory, and idea production within a single activated ``image'' (where an image can be thought of as a category of ideas). This model makes predictions, one of the most important being that an idea is more likely to be followed by an idea in the same category than would be expected by chance. Their model also predicts that new ideas in the same category as the previous idea are generated faster than ideas between categories. Nijstad and Stroebe verified these predictions in the context of nominal brainstorming.

@@

The most common approach to measure novelty and appropriateness is to ask domain experts to subjectively make scale-rated assessment of each \cite{lewis2011affective, amabile_1983}. These two measures are sometimes combined into one measure of quality \cite{little2010exploring}.
Some researchers opt for a measure that can be derived objectively. For example, Jansson et al. used `o' scores, derived from the frequency with which an idea occurs, to evaluate novelty \cite{jansson_design_1991}. We adopt this use of o-score in our later analyses.

Flexibility is often measured by the number of explored ``categories'' in a design space, or by subjective rating from domain experts \cite{lewis2011affective, marsh1996examples}. Category or feature-based quantities yield metrics such as within-categories fluency and length of train-of-thought when participants focus on a particular category \cite{nijstad_how_2006}. Building in this past line of work, we consider both individual ideas and categories of ideas.

\subsection{Crowdsourced Brainstorming}
The simplest imaginable instantiation of brainstorming in a microtask marketplace mirrors that of nominal brainstorming. More sophisticated environments are possible, such as those that forward ideas that others have generated (electronic brainstorming). 
%Examples for these environments are platforms for generating social innovation ideas or product concepts like OpenIDEO, Quirky and Threadless that employ structured process where participants take on different responsibility from generating ideas to evaluating others' ideas.
We constrain our focus to nominal brainstorming in this environment with the goal of establishing baselines.

While we are unaware of specific studies of brainstorming in microtask marketplaces, there is a range of related research examining other creative processes \cite{lewis2011affective, kittur2011crowdforge, Zhang:2012:HCT:2207676.2207708}. For example, Yu and Nickerson created an evolutionary crowd algorithm to generate creative chair designs \cite{yu_cooks_2011}. Their work demonstrates the creative potential of the crowd, but does not specifically address brainstorming or processes in which participants generate many ideas.

Little et el. compared the iterative and parallel human computation processes on a brainstorming task for names for fabricated companies \cite{little2010exploring}. In the iterative condition, participants saw all names suggested by previous participants. Participants in the parallel condition worked in isolation without seeing other participants' ideas. The parallel process was found to be more likely to generate names with high ratings, advocating the case for nominal brainstorming. The study did not mention categorization of generated ideas, an important measure on flexibility of idea generation \cite{lewis2011affective, nijstad_how_2006, finke1992creative, shah2003metrics}. Each participant also generated only five ideas, leaving the number of ideas requested per participant an open dimension to be explored.

The nature of the microtask marketplace may also require alternative ways of structuring the brainstorming activity.
% calls for an alternative structure for brainstorming tasks in this setting. Researchers have found that 30\% or more submission on Mechanical Turk may be low quality \cite{kittur2008crowdsourcing}. For example, submissions to a brainstorming task for a company name are sometimes grammartically awkward or offensive \cite{little2010exploring}. These low quality responses were not found in walk-in brainstorming studies. 
For example, Bernstein et al. found high variance of effort from Amazon Mechanical Turk workers \cite{soylent}. They characterized two worker personas at opposite ends of the effort spectrum: the {\em Eager Beaver\/} who goes beyond task requirement and the {\em Lazy Turker\/} who does as little work as necessary. Given this finding, a brainstorming task that asks participants to generate as many ideas as they can in a fixed time period might not be cost-effective, since a {\em Lazy Turker\/} can simply fill in a few ideas and wait for the time to run out instead of exerting full effort.

@@

In summary, while brainstorming has been examined in traditional and electronic settings, its application in crowd marketplaces has received limited attention, leaving open questions.

### 2013-10-17 chi2014/results.tex
10 page revision first attempt

We model this quantity using the following exponential model:
\[n_{ideas} = y_{scale} * x^{rate}\]
where $n_{ideas}$ represents the number of unique ideas, $y_{scale}$ serves to scale the model, $x$ is the response number, and $rate$ models the rate of novel ideas. Importantly, this simplified model does not model either the condition or the effects of workers. In our analysis of the data, we found that individual workers introduced considerable variation, preventing us from separating the effects of the condition from the worker. Accordingly, we only consider this simplified model.

@@

The visibly lower rate of growth for novel categories growth suggests workers are more likely to produce new ideas within existing categories, rather than create both novel ideas that also represent novel categories. We more closely examine characteristics of individuals' brainstorming runs next.

@@

\subsubsection{Most Popular Ideas}
Our data suggest that individuals typically produce ideas from a common set of idea categories early in the brainstorming process, then diverge and produce more original ideas. This phenomenon can be observed by examining the o-scores of ideas and idea categories.

Figures~\ref{fig:idea_oscore_order} and \ref{fig:cat_oscore_order} show the o-scores for response instances and idea categories, within a sliding window of size 10. Each point represents the mean o-score within that sliding window, with standard error bars provided for each point.

@@

These graphs lend support for hypothesis 2, the notion that there is a set of general, common ideas that make up the first several responses of every crowd brainstorming session, regardless of condition.

To more explicitly confirm this hypothesis, we extracted the top 5\% most common ideas (66 in total). If individuals are more likely to initially generate the same set of ideas, the top 5\% of the ideas should be more likely to appear in the first five instances of a run than they are to appear in any of the following instances. We introduce two Bernoulli random variables to model this. The first, defined by parameter $\theta_f$ represents the probability that a response instance is in the top 5\% most common ideas, given it is found in the first five instances of a run (i.e., $P(\theta_f|top)$). The second, defined by parameter $\theta_l$, is the probability that an instance is in the top \% given it is one of the \emph{last} ($\textgreater5$) instances in a run (i.e., $P(\theta_l|\overline{top})$).

We fit these parameters using data from all runs that have more than 10 responses. We chose this constraint so that no run could contribute evidence to $\theta_f$ without also contributing to $\theta_l$. Using an uninformative beta prior, the resulting parameters are $\theta_f = 0.56$ (95\% HDI 0.52-0.61) and $\theta_l = 0.32$ (95\% HDI 0.30-0.34). This difference is significant, supporting the hypothesis that common ideas are over-represented in the early part of a brainstorming run.

@@

Partitioning the data into instances $\leq20$ and $\textgreater20$, we found that these distributions of o-scores are best modeled using beta distributions. Figures~\ref{fig:idea_oscore_hyp4} and \ref{fig:cat_oscore_hyp4} show the data and fitted models. Examining the HDIs of the resultant model parameters shows significant differences between the models, confirming hypothesis 3.

Collectively, these results provide a clear guideline for maximizing originality in brainstorming tasks on microtask marketplaces: it is more cost-effective to solicit $\textgreater20$ ideas from a smaller pool of participants than to ask for fewer ideas from more individuals.

@@

\subsection{Idea Generation Patterns}
Given the clear differences in idea characteristics as a function of response number, we now consider idea generation patterns observable from the data. In this section, we examine these patterns in the context of hypotheses 4 and 5, the hypotheses that draw upon the SIAM model of brainstorming. This model predicts individuals will generate ideas within ``images'' or categories of ideas (i.e., ``riff'' on an idea or concept) before switching to a new category.

@@

We model the probability of any idea category being followed by the same idea category with a Bernoulli random variable. Using a uniform beta prior, we find the probability of a response instance being in the same idea category as the previous to be 15.6\% (HDI 14.3\% - 17.0\%). To establish a baseline to understand whether this probability is greater than chance, the most popular category tree in our data set is \emph{music player}, representing 5.65\% of all instances. Thus, an upper bound on the greatest probability of an instance being in the same category as the previous instance, by chance, is 5.65\%, well below the 14.3\% lower bound of the calculated HDI. Thus, we accept the hypothesis that an instance follows a previous instance in the same category with greater probability than is explained by random chance.

>>>>

We model this quantity using the following exponential model:
\[n_{ideas} = y_{scale} * x^{rate}\]
where $n_{ideas}$ represents the number of unique ideas, $y_{scale}$ serves to scale the model, $x$ is the response number, and $rate$ models the rate of novel ideas. Importantly, this model does not model either the condition or the effects of workers. In our analysis of the data, we found that individual workers introduced considerable variation, preventing us from separating the effects of the condition from the worker. Accordingly, we only consider this simplified model.

@@

The visibly lower rate of growth for novel categories suggests workers are more likely to produce new ideas within existing categories, rather than create both novel ideas that also represent novel categories. We more closely examine characteristics of individuals' brainstorming runs next.

@@

\subsubsection{Most Popular Ideas}

Figures~\ref{fig:idea_oscore_order} and \ref{fig:cat_oscore_order} show the o-scores for response instances and idea categories, within a sliding window of size 10. Each point represents the mean o-score within that sliding window, with standard error bars.

@@

This lends support for hypothesis 2, the notion that there is a set of general, common ideas that make up the first several responses of every crowd brainstorming session, regardless of condition.

To confirm this hypothesis, we extracted the top 5\% most common ideas (66 in total). If individuals are more likely to initially generate the same set of ideas, the top 5\% of the ideas should be more likely to appear in the first five instances of a run than they are to appear in any of the following instances. We introduce two Bernoulli random variables to model this. The first, defined by parameter $\theta_f$ represents the probability that a response instance is in the top 5\% most common ideas, given it is found in the first five instances of a run (i.e., $P(\theta_f|first)$). The second, defined by parameter $\theta_l$, is the probability that an instance is in the top \% given it is one of the \emph{last} ($\textgreater5$) instances in a run (i.e., $P(\theta_l|\overline{first})$).

We fit these parameters using data from all runs that have more than 10 responses. We chose this constraint so that no run could contribute evidence to $\theta_f$ without also contributing to $\theta_l$. Using an uninformative beta prior, the resulting parameters are $\theta_f = 0.56$ (HDI 0.52-0.61) and $\theta_l = 0.32$ (HDI 0.30-0.34). This difference is significant, supporting the hypothesis that common ideas are over-represented in the early part of a brainstorming run.

@@

Partitioning the data into instances $\leq20$ and $\textgreater20$, we found that these distributions of o-scores are best modeled using beta distributions. Figures~\ref{fig:idea_oscore_hyp4} and \ref{fig:cat_oscore_hyp4} show the data and fitted models. We found significant differences between model parameters, confirming hypothesis 3.

Collectively, these results provide a guideline for maximizing originality in brainstorming tasks on microtask marketplaces: it is more effective to solicit $\textgreater20$ ideas from a smaller pool of participants than to ask for fewer ideas from more individuals.

@@

\subsection{Idea Generation Patterns}
Given the differences in originality and rarity as a function of response number, we now consider idea generation patterns observable from the data. We examine these patterns in the context of hypotheses 4 and 5, which draw upon the SIAM model of brainstorming. This model predicts individuals will generate ideas within ``images'' or categories of ideas (i.e., ``riff'' on an idea or concept) before switching to a new category.

@@

We model the probability of any idea category being followed by the same idea category with a Bernoulli random variable. Using a uniform beta prior, we find the probability of a response instance being in the same idea category as the previous to be 15.6\% (HDI 14.3\% - 17.0\%). To understand whether this probability is greater than chance, we use the most popular category tree in our data set (\emph{music player}), representing 5.65\% of all instances as an upper bound. This well below the 14.3\% lower bound of the calculated HDI. Thus, we accept the hypothesis that an instance follows a previous instance in the same category with greater probability than is explained by random chance.
